### 2019-02-15 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Pas mal relu le Chapitre 5, écrit un abstract.

\TODOL{This chapter is basically a raw include from my paper ``Multi-Player Bandits Revisited'', see https://hal.inria.fr/hal-01629733}

Multi-player Multi-Armed Bandits (MAB) have been extensively studied in the literature, motivated by applications to Cognitive Radio systems.
Driven by such applications as well, we motivate the introduction of several levels of feedback for multi-player MAB algorithms. Most existing work assume
that \emph{sensing information} is available to the algorithm. Under this assumption, we improve the state-of-the-art lower bound for the regret of any decentralized algorithms
and introduce two algorithms, \RandTopM{} and \MCTopM{}, that are shown to empirically outperform existing algorithms. Moreover, we provide strong theoretical guarantees for these algorithms, including
a notion of asymptotic optimality in terms of the number of selections of bad arms.
We then introduce a promising heuristic, called \Selfish{}, that can operate
without sensing information, which is crucial for emerging applications to Internet of Things networks. We investigate the empirical performance of this algorithm
and provide some first theoretical elements for the understanding of its behavior.

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\section{Introduction}
\label{sec:5:introduction}
% the paragraph below may be useful to state in the intro or early in the paper

% general intro, UCB

Several sequential decision making problems under the constraint of partial information
have been studied since the 1950s under the name of Multi-Armed Bandit (MAB) problems \citep{Robbins52,LaiRobbins85}.
In a stochastic MAB model, an agent is facing $K$ unknown probability distributions, called arms in reference to the arms of a one-armed bandit (or slot machine) in a casino.
Each time she selects (or draws) an arm, she receives a reward drawn from the associated distribution.
Her goal is to build a sequential selection strategy that maximizes the total reward received.
A class of algorithms to solve this problem is based on Upper Confidence Bounds (UCB), first proposed by \cite{LaiRobbins85,Agrawal95} and further popularized by \cite{Auer02}.
The field has been very active since then, with several algorithms proposed and analyzed, both theoretically and empirically, even beyond the stochastic assumption on arms, as explained in the survey by \cite{Bubeck12}.

% appli, from clinical trials to cognitive radios

The initial motivation to study MAB problems arose from clinical trials (the first MAB model can be traced back to $1933$, by \citeauthor{Thompson33}), in which a doctor sequentially allocates treatments (arms) to patients and observes their efficacy (reward).
More recently, applications of MAB have shifted towards sequential content recommendation, \eg{} sequential display of advertising to customers or A/B testing \citep{Li10,Chapelleetal14Ad}.
%
In the mean time, MAB were found to be relevant to the field of Cognitive Radio (CR, \cite{Mitola99}),
and \cite{Jouini09,Jouini10} first proposed to use \UCB{} for the Opportunistic Spectrum Access (OSA) problem,
and successfully conducted experiments on real radio networks demonstrating its usefulness.
For CR applications, each arm models the quality or availability of a radio channel (a frequency band) in which there is some background traffic (\eg, primary users paying to have a guaranteed access to the channel in the case of OSA).
A smart radio device needs to insert itself in the background traffic, by sequentially choosing a channel to access and try to communicate on, seeking to optimize the quality of its global transmissions.

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\section{Multi-Player Bandit Model with Different Feedback Levels}
\label{sec:5:model}

@@

A multi-player MAB strategy is a tuple $\rho = (\rho^1,\dots,\rho^M)$ of arm selection strategies for each player, and the goal is to propose a strategy that maximizes the total reward of the system, under some constraints.
First, each player $j$ should adopt a \emph{sequential} strategy $\rho^j$, that decides which arm to select at time $t$ based on \emph{previous observations}.
Previous observations for player $j$ at time $t$ always include the previously chosen arms $A^j(s)$ and received rewards $r^j(s)$ for $s<t$, but may also include the \emph{sensing information} $Y_{A^j(t),t}$ or the \emph{collision information} $C^j(t)$.
More precisely, depending on the application, one may consider the following three observation models, \modelun, \modeldeux{} and \modeltrois.
%
% If the arms have continuous distributions (or are such that  $\Pr(Y_{k,s}=0)=0$), the \emph{sensing information} $Y_{A^j(t),t}$ and \emph{collision information} $C^j(t)$ can always be extracted from the reward information. But for Bernoulli distribution, one may consider the following three observation models, that are not equivalent:
\begin{itemize}
  \item[\modelun]
    \textbf{Simultaneous sensing and collision}: player $j$ observes  $Y_{A^j(t),t}$ \emph{and} $C^j(t)$ (not previously studied).
  \item[\modeldeux]
    \textbf{Sensing, then collision}: player $j$ observes $Y_{A^j(t),t}$, \emph{then} observes the reward, and thus also $C^j(t)$ only if $Y_{A^j(t),t} = 1$.
    This common setup, studied for example by \cite{Anandkumar11,Avner15,Rosenski16}, is relevant to model the OSA problem: the device first checks for the presence of primary users in the chosen channel.
    If this channel is free ($Y_{A^j(t),t}=1$), the transmission is successful ($r^j(t)=1$) if no collision occurs with other smart devices ($\overline{C^j(t)}$).
  \item[\modeltrois]
    \textbf{No sensing}: player $j$ only observes the reward $r^j(t)$.
    For IoT networks, this reward can be interpreted as an acknowledgement from a Base Station,
    received when a communication was successful.
    A lack of acknowledgment may be due to a collision
    with a device from the background traffic $(Y_{A^j(t),t}=0)$,
    or to a collision with one of the others players ($C^j(t)$).
    However, the sensing and collision information are censored.
    Recently, \cite{Bonnefoi17} presented the first (bandit-based) algorithmic solutions under this (harder) feedback model, in a slightly different setup, more suited to large scale IoT applications. %\footnote{\cite{Bonnefoi17} considers a different setting, more suited for large-scale IoT networks, and a future work will be to extend our work to this setting with more than $K$ players but small probability of activations.}.
\end{itemize}
\noindent Under each of these three models, we define $\cF^j_t$ to be the filtration generated by the observations gathered by player $j$ up to time $t$ (which contains different information under models \modelun, \modeldeux{} and \modeltrois).
While a \emph{centralized} algorithm may select the vector of actions for all players $(A^1(t),\dots,A^M(t))$ based on all the observations from $\bigcup_j \cF^j_{t-1}$, under a \emph{decentralized} algorithm the arm selected at time $t$ by player $j$ only depends on the past observation of this player.
More formally, $A^j(t)$ is assumed to be $\cF^j_{t-1}$-measurable.

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\section{An Asymptotic Regret Lower Bound}
\label{sec:5:lowerbound}

@@

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\section{New Algorithms for Multi-Player Bandits}
\label{sec:5:algorithms}

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\section{Empirical performances}
\label{sec:5:experiments}

@@

We illustrate here the empirical performances of the algorithms presented in Section~\ref{sec:5:algorithms}, used in combination with the \klUCB{} indices. %used with two index policies, \UCB{} and \klUCB.
Some plots are at pages \pageref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} and \pageref{fig:5:MP__K9_M6_T10000_N1000__4_algos} and most of them in Appendix~\ref{app:5:plotsFromSec5}.
% but observations and conclusions from the experiments are discussed here.

In experiments that are not reported here, we could observe that using \klUCB{} rather than \UCB{} indices always yield better practical performance.
%, as the theoretical guarantees for single player suggested,
As the prupose of this work is not to optimize on the index policy, but rather propose new ways of using indices in a decentralized setting,
% And for some configurations, using a decentralized approach with a more efficient index family (\klUCB{} instead of \UCB) has better performances than the centralized approach.
we only report results for \klUCB.
In a first set of experiments, \MCTopM{}, \RandTopM{} and \Selfish{} are benchmarked against the state-of-the-art \RhoRand{} algorithm.
We also include a centralized multiple-play \klUCB{} algorithm,
%as defined by \cite{Anantharam87a},
essentially to check that the \emph{``price of decentralized learning''} is not too large.

@@

%
% Regular plots of centralized regrets
%
\begin{figure}[!h]
  \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
    \includegraphics[width=0.8\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled]{Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \rhoRand{} (top \textcolor{blue}{blue} curve) is outperformed by the other algorithms (and the gain increases with $M$). \MCTopM{} (bottom \textcolor{gold}{yellow}) outperforms all the other algorithms is most cases.}
  % \label{fig:5:MP__K9_M2-6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  \label{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\section{Theoretical elements}
\label{sec:5:upperbounds}

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\section{Conclusion and future work}
\label{sec:5:conclusion}

>>>>

Multi-player Multi-Armed Bandits (MAB) have been extensively studied in the literature, motivated by applications to Cognitive Radio systems.
Driven by such applications as well, we motivate the introduction of several levels of feedback for multi-player MAB algorithms.
Existing works assume that \emph{sensing information} is available to the algorithm. Under this assumption, we improve the state-of-the-art lower bound for the regret of any decentralized algorithms of a certain class.
We introduce two algorithms, \RandTopM{} and \MCTopM{}, that are shown to empirically outperform existing algorithms. Moreover, we provide strong theoretical guarantees for these algorithms, including
a notion of asymptotic optimality in terms of the number of selections of bad arms.
We then introduce a promising heuristic, called \Selfish{}, that can operate
without sensing information, which is crucial for emerging applications to Internet of Things networks. We investigate the empirical performance of this algorithm
and provide some first theoretical elements for the understanding of its behavior.

% -----------------------------------------------------------------
\section{Motivation for multi-player MAB models}
\label{sec:5:introduction}
% -----------------------------------------------------------------

% % general intro, UCB

% Several sequential decision making problems under the constraint of partial information
% have been studied since the 1950s under the name of Multi-Armed Bandit (MAB) problems \citep{Robbins52,LaiRobbins85}.
% In a stochastic MAB model, an agent is facing $K$ unknown probability distributions, called arms in reference to the arms of a one-armed bandit (or slot machine) in a casino.
% Each time she selects (or draws) an arm, she receives a reward drawn from the associated distribution.
% Her goal is to build a sequential selection strategy that maximizes the total reward received.
% A class of algorithms to solve this problem is based on Upper Confidence Bounds (UCB), first proposed by \cite{LaiRobbins85,Agrawal95} and further popularized by \cite{Auer02}.
% The field has been very active since then, with several algorithms proposed and analyzed, both theoretically and empirically, even beyond the stochastic assumption on arms, as explained in the survey by \cite{Bubeck12}.

% % appli, from clinical trials to cognitive radios

% The initial motivation to study MAB problems arose from clinical trials (the first MAB model can be traced back to $1933$, by \citeauthor{Thompson33}), in which a doctor sequentially allocates treatments (arms) to patients and observes their efficacy (reward).
% More recently, applications of MAB have shifted towards sequential content recommendation, \eg{} sequential display of advertising to customers or A/B testing \citep{Li10,Chapelleetal14Ad}.
% %
% In the mean time, MAB were found to be relevant to the field of Cognitive Radio (CR, \cite{Mitola99}),
% and \cite{Jouini09,Jouini10} first proposed to use \UCB{} for the Opportunistic Spectrum Access (OSA) problem,
% and successfully conducted experiments on real radio networks demonstrating its usefulness.
% For CR applications, each arm models the quality or availability of a radio channel (a frequency band) in which there is some background traffic (\eg, primary users paying to have a guaranteed access to the channel in the case of OSA).
% A smart radio device needs to insert itself in the background traffic, by sequentially choosing a channel to access and try to communicate on, seeking to optimize the quality of its global transmissions.

@@

% -----------------------------------------------------------------
\section{Multi-Player Bandit Model with Different Feedback Levels}
\label{sec:5:model}
% -----------------------------------------------------------------

@@

A multi-player MAB strategy is a tuple $\rho = (\rho^1,\dots,\rho^M)$ of arm selection strategies for each player, and the goal is to propose a strategy that maximizes the total reward of the system, under some constraints.
First, each player $j$ should adopt a \emph{sequential} strategy $\rho^j$, that decides which arm to select at time $t$ based on \emph{previous observations}.
Previous observations for player $j$ at time $t$ always include the previously chosen arms $A^j(s)$ and received rewards $r^j(s)$ for $s<t$, but may also include the \emph{sensing information} $Y_{A^j(t),t}$ or the \emph{collision information} $C^j(t)$.
More precisely, depending on the application, one may consider the following three observation models, \modelun, \modeldeux{} and \modeltrois.
%
% If the arms have continuous distributions (or are such that  $\Pr(Y_{k,s}=0)=0$), the \emph{sensing information} $Y_{A^j(t),t}$ and \emph{collision information} $C^j(t)$ can always be extracted from the reward information. But for Bernoulli distribution, one may consider the following three observation models, that are not equivalent:
\begin{itemize}
  \item[\modelun]
    \textbf{Simultaneous sensing and collision}: player $j$ observes  $Y_{A^j(t),t}$ \emph{and} $C^j(t)$ (not previously studied).
  \item[\modeldeux]
    \textbf{Sensing, then collision}: player $j$ observes $Y_{A^j(t),t}$, \emph{then} observes the reward, and thus also $C^j(t)$ only if $Y_{A^j(t),t} = 1$.
    This common setup, studied for example by \cite{Anandkumar11,Avner15,Rosenski16}, is relevant to model the OSA problem: the device first checks for the presence of primary users in the chosen channel.
    If this channel is free ($Y_{A^j(t),t}=1$), the transmission is successful ($r^j(t)=1$) if no collision occurs with other smart devices ($\overline{C^j(t)}$).
  \item[\modeltrois]
    \textbf{No sensing}: player $j$ only observes the reward $r^j(t)$.
    For IoT networks, this reward can be interpreted as an acknowledgement from a Base Station,
    received when a communication was successful.
    A lack of acknowledgment may be due to a collision
    with a device from the background traffic $(Y_{A^j(t),t}=0)$,
    or to a collision with one of the others players ($C^j(t)$).
    However, the sensing and collision information are censored.
    Recently, our work presented in Chapter~\ref{chapter:4} \cite{Bonnefoi17} presented the first (bandit-based) algorithmic solutions under this (harder) feedback model, in a slightly different setup, more suited to large scale IoT applications. %\footnote{\cite{Bonnefoi17} considers a different setting, more suited for large-scale IoT networks, and a future work will be to extend our work to this setting with more than $K$ players but small probability of activations.}.
\end{itemize}
\noindent Under each of these three models, we define $\cF^j_t$ to be the filtration generated by the observations gathered by player $j$ up to time $t$ (which contains different information under models \modelun, \modeldeux{} and \modeltrois).
While a \emph{centralized} algorithm may select the vector of actions for all players $(A^1(t),\dots,A^M(t))$ based on all the observations from $\bigcup_j \cF^j_{t-1}$, under a \emph{decentralized} algorithm the arm selected at time $t$ by player $j$ only depends on the past observation of this player.
More formally, $A^j(t)$ is assumed to be $\cF^j_{t-1}$-measurable.

@@

% -----------------------------------------------------------------
\section{An Asymptotic Regret Lower Bound for a certain class of algorithms}
\label{sec:5:lowerbound}
% -----------------------------------------------------------------

\TODOL{Rewrite this to include new knowledge presented in Appendix of \cite{KaufmannAbbas19}.}

@@

\TODOL{Rewrite this to include new knowledge presented in Appendix of \cite{KaufmannAbbas19}.}

@@

% -----------------------------------------------------------------
\section{New Algorithms for Multi-Player Bandits}
\label{sec:5:algorithms}
% -----------------------------------------------------------------

@@

% -----------------------------------------------------------------
\section{Empirical performances}
\label{sec:5:experiments}
% -----------------------------------------------------------------

@@

We illustrate here the empirical performances of the algorithms presented in Section~\ref{sec:5:algorithms}, used in combination with the \klUCB{} indices.
Some plots are at pages \pageref{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems} and \pageref{fig:5:MP__K9_M6_T10000_N1000__4_algos} and most of them in Appendix~\ref{app:5:plotsFromSec5}.

\TODOL{Rewrite appendix to include all simulations here!}

\TODOL{Include here some plots showing \RhoRand{} with \UCB{} and \klUCB{} vs \MCTopM{} with \UCB{} and \klUCB{}.}

In experiments that are not reported here, we could observe that using \klUCB{} rather than \UCB{} indices always yield better practical performance.
%, as the theoretical guarantees for single player suggested,
As the purpose of this work is not to optimize on the index policy, but rather propose new ways of using indices in a decentralized setting,
% And for some configurations, using a decentralized approach with a more efficient index family (\klUCB{} instead of \UCB) has better performances than the centralized approach.
we only report results for \klUCB.
In a first set of experiments, \MCTopM{}, \RandTopM{} and \Selfish{} are benchmarked against the state-of-the-art \RhoRand{} algorithm.
We also include a centralized multiple-play \klUCB{} algorithm,
%as defined by \cite{Anantharam87a},
essentially to check that the \emph{``price of decentralized learning''} is not too large.

@@

%
% Regular plots of centralized regrets
%
\begin{figure}[!h]
  \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
    \includegraphics[width=1.00\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled]{Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \rhoRand{} (top \textcolor{blue}{blue} curve) is outperformed by the other algorithms (and the gain increases with $M$). \MCTopM{} (bottom \textcolor{gold}{yellow}) outperforms all the other algorithms is most cases.}
  % \label{fig:5:MP__K9_M2-6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  \label{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

% -----------------------------------------------------------------
\section{Theoretical elements}
\label{sec:5:upperbounds}
% -----------------------------------------------------------------

@@

% -----------------------------------------------------------------
\section{Conclusion and future work}
\label{sec:5:conclusion}
% -----------------------------------------------------------------

### 2019-02-15 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
Pas mal relu le Chapitre 5, écrit un abstract.

Recall that we want to upper bound
$ (b) : = \sum_{k \in \Mbest} (\mu_k - \mu_{M*}) \left(T - \E_{\mu}[T_k(T)]\right)$.
First, we observe that, for all $k\in \Mbest$,
\begin{eqnarray*}
T - \E_{\mu}[T_k(T)] & \leq & T - \E_{\mu}\left[\sum_{t=1}^T \indic(\exists j : A^j(t) = k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(\forall j, A_j(t) \neq k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(k \notin \widehat{S}_t)\right],\end{eqnarray*}
where we denote by $\widehat{S}_t = \{A^j(t), j \in \{1,\dots,M\}\}$ the set of selected arms at time $t$ (with no repetition). With this notation one can write
\begin{eqnarray*}
 (b) & \leq & (\mu_1 - \mu_{M^*})  \sum_{k \in \Mbest} \left(T - \E_{\mu}[T_k(T)]\right) \leq  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[\sum_{k \in \Mbest} \sum_{t = 1}^T \indic(k \notin \widehat{S}_t)\right] \\
 & = &  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right].
\end{eqnarray*}
The quantity $\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)$ counts the number of optimal arms that have not been selected at time $t$. For each mis-selection of an optimal arm, there either exists a sub-optimal arm that has been selected, or an arm in $\Mbest$ on which a collision occurs. Hence
\[\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t) = \sum_{k \in \Mbest}\indic(C_k(t)) + \sum_{k \in \Mworst} \indic(\exists j : A^j(t) = k),\]
which yields
\[\E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right] \leq \sum_{k \in \Mbest}\E_{\mu}\left[\cC_k(T)\right] + \sum_{k \in \Mworst} \E_{\mu}\left[T_k(T)\right]\]
and Lemma~\ref{lem:5:1stUpperBound} follows.

@@

@@

@@

\begin{figure}[h!]
  \begin{tikzpicture}[>=latex',line join=bevel,scale=3.8]
      %
      \node (start) at (1.5,0.30) {$(0)$ Start $t=0$};
      \node (notfixed) at (1,0) [draw,rectangle,thick] {Not fixed, $\overline{s^j(t)}$};
      \node (fixed) at (0,0) [draw,rectangle,thick] {Fixed, $s^j(t)$};
      %
      \draw [black,->] (start) -> (notfixed.20);
      \draw [color=cyan,thick,->] (notfixed) to[bend right] node[midway,above,text width=5cm,text centered,black] {\small $(1)$ $\overline{C^j(t)}, A^j(t) \in \TopM(t)$} (fixed);
      \path [color=blue,thick,->] (notfixed) edge[loop right] node[right,text width=4cm,text badly centered,black] {\small $(2)$  $C^j(t), A^j(t) \in \TopM(t)$} (1);
      \path [color=red,thick,->] (notfixed) edge[loop below] node[below,text centered,black] {\small $(3)$  $A^j(t) \notin \TopM(t)$} (1);
      \path [color=darkgreen,thick,->] (fixed) edge[loop left] node[left,text width=2.9cm,text badly centered,black] {\small $(4)$ $A^j(t) \in \TopM(t)$} (fixed);
      \draw [color=red,thick,->] (fixed) to[bend right] node[midway,below,text centered,black] {\small $(5)$  $A^j(t) \notin \TopM(t)$} (notfixed);
      %
  \end{tikzpicture}
  \caption[``State-machine'' representation of \MCTopM]{Player $j$ using \MCTopM, represented as ``state machine'' with $5$ transitions.
  Taking one of the five transitions means playing one round of the Algorithm~\ref{algo:5:MCTopM}, to decide $A^j(t+1)$ using information of previous steps.}
  \label{fig:5:StateMachineAlgorithm_MCTopM}
\end{figure}

@@

@@

We wrote a script
\footnote{\url{banditslilian.gforge.inria.fr/docs/complete_tree_exploration_for_MP_bandits.html}}
that explores formally all the possible runs,
up-to a certain small time horizon,
by exploring the complete \emph{game tree},
of possible (random) rewards from the $K$ arms
and (random) actions from the $M$ players, up-to a small depth of let say $T=8$.
%
Such game tree becomes quickly very large, but this was enough to confirm that with
a certain small probability, function of $\mu_1,\dots,\mu_K$,
two players can arrive in just a few steps in a ``bad'' absorbing configuration.
%
For instance, for only $K=2$ arms, the following game tree in Figure~\ref{fig:5:oneGameTree_SelfishKLUCB} illustrates the first $3$ steps that can lead to $2$ absorbing configurations.
Using symbolic computations, the probability of reaching any of them was found to be
$\geq \mu_1^2(1-\mu_2)^2/2 + \mu_2^2(1-\mu_1)^2/2$ for \Selfish-\UCB.
That is far from being negligible, as it evaluates to $0.328$ for $\boldsymbol{\mu} = [0.1, 0.5, 0.9]$,
and a numerical simulation on $1000$ runs found $325$ cases of bad performance.
%
The same game tree exploration can be made for \Selfish-\klUCB,
but so far we were not able to justify why it experiences fewer cases of bad performances even though our software found the same (lower bound on) failure probability.

@@

>>>>

Recall that we want to upper bound
$ (b) : = \sum_{k \in \Mbest} (\mu_k - \mu_{M*}) \left(T - \E_{\mu}[T_k(T)]\right)$.
First, we observe that, for all $k\in \Mbest$,
\begin{eqnarray*}
  T - \E_{\mu}[T_k(T)] & \leq T - \E_{\mu}\left[\sum_{t=1}^T \indic(\exists j : A^j(t) = k)\right] \\
  & = \E_{\mu}\left[\sum_{t=1}^T \indic(\forall j, A_j(t) \neq k)\right] = \E_{\mu}\left[\sum_{t=1}^T \indic(k \notin \widehat{S}_t)\right],
\end{eqnarray*}
where we denote by $\widehat{S}_t = \{A^j(t), j \in \{1,\dots,M\}\}$ the set of selected arms at time $t$ (with no repetition). With this notation one can write
\begin{eqnarray*}
 (b) & \leq & (\mu_1 - \mu_{M^*})  \sum_{k \in \Mbest} \left(T - \E_{\mu}[T_k(T)]\right) \leq  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[\sum_{k \in \Mbest} \sum_{t = 1}^T \indic(k \notin \widehat{S}_t)\right] \\
 & = &  (\mu_1 - \mu_{M^*})  \E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right].
\end{eqnarray*}
The quantity $\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)$ counts the number of optimal arms that have not been selected at time $t$. For each mis-selection of an optimal arm, there either exists a sub-optimal arm that has been selected, or an arm in $\Mbest$ on which a collision occurs. Hence
\[\sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t) = \sum_{k \in \Mbest}\indic(C_k(t)) + \sum_{k \in \Mworst} \indic(\exists j : A^j(t) = k),\]
which yields
\[\E_{\mu}\left[ \sum_{t = 1}^T \sum_{k \in \Mbest}\indic(k \notin \widehat{S}_t)\right] \leq \sum_{k \in \Mbest}\E_{\mu}\left[\cC_k(T)\right] + \sum_{k \in \Mworst} \E_{\mu}\left[T_k(T)\right]\]
and Lemma~\ref{lem:5:1stUpperBound} follows.

@@

\TODOL{This is wrong as explained in \cite{BoursierPerchet18}! Rewrite this to include new knowledge presented in Appendix of \cite{KaufmannAbbas19}.}

@@

\TODOL{I should include this in the main text, it makes more sense to present RandTopM and then MCTopM !}

@@

\begin{figure}[h!]
  \resizebox{0.98\textwidth}{!}{
  \begin{tikzpicture}[>=latex',line join=bevel,scale=5]
      %
      \node (start) at (1.5,0.30) {$(0)$ Start $t=0$};
      \node (notfixed) at (1,0) [draw,rectangle,thick] {Not fixed, $\overline{s^j(t)}$};
      \node (fixed) at (0,0) [draw,rectangle,thick] {Fixed, $s^j(t)$};
      %
      \draw [black,->] (start) -> (notfixed.20);
      \draw [color=cyan,thick,->] (notfixed) to[bend right] node[midway,above,text width=5cm,text centered,black] {\small $(1)$ $\overline{C^j(t)}, A^j(t) \in \TopM(t)$} (fixed);
      \path [color=blue,thick,->] (notfixed) edge[loop right] node[right,text width=4cm,text badly centered,black] {\small $(2)$  $C^j(t), A^j(t) \in \TopM(t)$} (1);
      \path [color=red,thick,->] (notfixed) edge[loop below] node[below,text centered,black] {\small $(3)$  $A^j(t) \notin \TopM(t)$} (1);
      \path [color=darkgreen,thick,->] (fixed) edge[loop left] node[left,text width=2.9cm,text badly centered,black] {\small $(4)$ $A^j(t) \in \TopM(t)$} (fixed);
      \draw [color=red,thick,->] (fixed) to[bend right] node[midway,below,text centered,black] {\small $(5)$  $A^j(t) \notin \TopM(t)$} (notfixed);
      %
  \end{tikzpicture}
  }
  \caption[``State-machine'' representation of \MCTopM]{Player $j$ using \MCTopM, represented as ``state machine'' with $5$ transitions.
  Taking one of the five transitions means playing one round of the Algorithm~\ref{algo:5:MCTopM}, to decide $A^j(t+1)$ using information of previous steps.}
  \label{fig:5:StateMachineAlgorithm_MCTopM}
\end{figure}

@@

\TODOL{Maybe we can completely remove this, and just points to the paper \cite{Besson2018ALT}?}

@@

We wrote a script
\footnote{~See online \texttt{\url{smpybandits.github.io/docs/complete_tree_exploration_for_MP_bandits.html}}}
that explores formally all the possible runs,
up-to a certain small time horizon,
by exploring the complete \emph{game tree},
of possible (random) rewards from the $K$ arms
and (random) actions from the $M$ players, up-to a small depth of let say $T=8$.
%
Such game tree becomes quickly very large, but this was enough to confirm that with
a certain small probability, function of $\mu_1,\dots,\mu_K$,
two players can arrive in just a few steps in a ``bad'' absorbing configuration.
%
For instance, for only $K=2$ arms, the following game tree in Figure~\ref{fig:5:oneGameTree_SelfishKLUCB} illustrates the first $3$ steps that can lead to $2$ absorbing configurations.
Using symbolic computations, the probability of reaching any of them was found to be
$\geq \mu_1^2(1-\mu_2)^2/2 + \mu_2^2(1-\mu_1)^2/2$ for \Selfish-\UCB.
That is far from being negligible, as it evaluates to $0.328$ for $\boldsymbol{\mu} = [0.1, 0.5, 0.9]$,
and a numerical simulation on $1000$ runs found $325$ cases of bad performance.
%
The same game tree exploration can be made for \Selfish-\klUCB,
but so far we were not able to justify why it experiences fewer cases of bad performances even though our software found the same (lower bound on) failure probability.

@@

\TODOL{Maybe we can not include this part and just points to the paper \cite{Besson2018ALT}?}
